---
title: "index"
author: "group 1"
date: "2022-11-14"
output: html_document
---

This is a data set that shows this this and this.

```{r trial, echo=FALSE, message=FALSE, results='asis'}
# This is just practicing whether the table will show up
library(knitr)
library(dplyr)
summary_table <- read.csv(file = "tiktok_and_spotify_popular.csv")
kable(summary_table[1:10, ])

```

## Summary Values <- rewrite as paragraph

```{r echo=FALSE, message = TRUE}
num_of_songs <- nrow(summary_table)

unique_artists <- summary_table %>% 
  group_by(artist_names) %>% 
  summarise(
    artist_name = unique(artist_names)
  )
num_of_artists <- nrow(unique_artists)
pop_both <- summary_table %>% 
  filter(artist_pop >= 0)
num_of_pop_both <- nrow(pop_both)

artist_trend <- summary_table %>% 
  filter(artist_pop >= 0) %>% 
  summarise(
    artist_names = unique(artist_names)
  )
num_of_trending_artists <- nrow(artist_trend)

most_popular_artist <- summary_table %>% 
  group_by(artist_names) %>% 
  summarize(
    num_of_songs =  length(unique(track_name))
  ) %>% 
  filter(num_of_songs == max(num_of_songs)) 

most_popular_artist_name <- most_popular_artist %>% 
  pull(artist_names)

most_popular_artist_song_num <- most_popular_artist %>% 
  pull(num_of_songs)

```




How many songs were analyzed? `r num_of_songs`

How many artists were analyzed? `r num_of_artists`

How many songs were trending on spotify were also trending on tiktok? `r num_of_pop_both`

How many artists were trending on Tiktok out of the Spotify charts? `r num_of_trending_artists`

How many songs did the most popular artist have trending on Tiktok? `r most_popular_artist_name`

How many songs did she have? `r most_popular_artist_song_num`


