---
title: "P2 Project Report"
author: "Mie, Xenia, Kim"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this file for?

* This file will eventually become your project report for **P02: Exploratory Data Analysis**. Specifically, you will write rmarkdown to report your exploratory data analysis.

* Please see Canvas for more details.

```{r trial, echo=FALSE, results='asis'}
library(knitr)
summary_table <- read.csv(file = "tiktok_and_spotify_popular.csv")
kable(summary_table[1:5, ])
```


```{r num_of_songs, echo=FALSE, results='asis'}
num_of_songs <- nrow(summary_table)
```

```{r num_of_artists, echo=FALSE, results='asis'}
library(dplyr)
unique_artists <- summary_table %>% 
  group_by(artist_names) %>% 
  summarise(
    artist_name = unique(artist_names)
  )
num_of_artists <- nrow(unique_artists)
```

```{r num_of_pop_both, echo=FALSE, results='asis'}

```

For our data analysis, we took a look at data from 2020 to 2021 regarding popular songs on Tiktok vs. the Billboard Charts. We analyzed `r num_of_songs` and `r num_of_artists` in total. 
How many songs were analyzed?
`r num_of_songs`

How many artists were analyzed?
`r num_of_artists`




data_access_test()
```
