---
title: "P2 Project Report"
author: "Mie, Xenia, Kim"
date: "11/14/2022"
output: html_document
---

This is a data set that shows this this and this.

```{r trial, echo=FALSE, message=FALSE, results='asis'}
# This is just practicing whether the table will show up
library(knitr)
library(dplyr)
summary_table <- read.csv(file = "tiktok_and_spotify_popular.csv")
kable(summary_table[1:10, ])

```

## Summary Values <- rewrite as paragraph

```{r echo=FALSE, message = TRUE}
num_of_songs <- nrow(summary_table)

unique_artists <- summary_table %>% 
  group_by(artist_names) %>% 
  summarise(
    artist_name = unique(artist_names)
  )
num_of_artists <- nrow(unique_artists)
pop_both <- summary_table %>% 
  filter(artist_pop >= 0)
num_of_pop_both <- nrow(pop_both)

artist_trend <- summary_table %>% 
  filter(artist_pop >= 0) %>% 
  summarise(
    artist_names = unique(artist_names)
  )
num_of_trending_artists <- nrow(artist_trend)

most_popular_artist <- summary_table %>% 
  group_by(artist_names) %>% 
  summarize(
    num_of_songs =  length(unique(track_name))
  ) %>% 
  filter(num_of_songs == max(num_of_songs)) 

most_popular_artist_name <- most_popular_artist %>% 
  pull(artist_names)

most_popular_artist_song_num <- most_popular_artist %>% 
  pull(num_of_songs)

```

For our data analysis, we took a look at data from 2020 to 2021 regarding popular songs on TikTok vs. the Spotify Charts. We analyzed `r num_of_songs` and `r num_of_artists` in total. We found there to be `r num_of_pop_both` songs that were trending on Spotify and TikTok. We then wondered how many artists were trending on Tiktok but not on the Spotify charts and found this number to be `r num_of_trending_artists`. The most popular artist trending on TikTok was `r most_popular_artist_name` and she had `r most_popular_artist_song_num` songs in total on the app.

The following table includes aggregated data from datasets which store information on the popular songs of TikTok and Spotify charts. 

We made many different observations after analyzing our table and discovered that there can be duplicates of songs depending on the album they're from. For example, we see "Driver's License" appear twice because it is paired with the album "Sour" as well as recorded as a single. We also observed the unique columns that such as peak_rank, artist_pop, and track_pop. Peak rank is the value of the highest ranking of the song on the Spotify charts, artist_pop is the artist's popularity (higher value = more popular), and track_pop is the song's popularity. We then utilized these columns to act as rankings in future summaries and charts. 

